\documentclass[a4paper, 11pt]{article}
\usepackage{comment} % enables the use of multi-line comments (\ifx \fi) 
\usepackage{lipsum} %This package just generates Lorem Ipsum filler text. 
\usepackage{fullpage} % changes the margin
\usepackage{hyperref}

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{Assignment 8} \hfill \textbf{Tyler Wilding} \\
\normalsize COSC 4426 \hfill Due Date: 18/09/16 \\
Prof. Biocchi \hfill -- \\
TA: -- \hfill \href{http://www.algomau.ca}{Website Used}

\section*{Passive Access Report for Algomau.ca}

\section*{Domain Information}
\begin{enumerate}
\item Website is using SSL from a certificate supplied by RapidSSL that is set to expire on August 22nd 2018.
\item The domain is registered through Rebel.ca Corp under the name Mr. DeConto and is set to expire on January 4th 2017 when running a WhoIS check. However when using netcraft the domain registrar is cira.ca registered under the University's name
\item The IP address is 161.47.16.90
\end{enumerate}

\section*{Hosting Information}
\begin{enumerate}
\item Algomau seems to run their own DNS servers, ns3.algomau.ca and ns4.algomau.ca.
\item The DNS admin's account is listed as its@algomau.ca.
\item These name servers are most likely provided by Rackspace, as this the hosting provider for the website.
\item The website is being hosted with nginx on Linux
\item Most of the most common ports are disabled, with only 80 and 443 being open.
\end{enumerate}

\section*{Website Details}
\begin{enumerate}
\item The website is making use of HTML version 5, most likely CSS version 3 as well as javascript.
\item PHP is the language of choice for both my.algomau.ca and the main pages due to wordpress.  
\item Because the website is running WordPress this also means they are using MySQL as a database.
\item Several google analytics cookies are used the website.
\item The website is also making use of javascript libraries such as jQuery and modernizr.
\item As mentioned previously, the website is using Google Analytics and while the main domain's account details are hidden, their subdomain my.algomau.ca's account information is UA-37063246-1.
\item Algomau.ca is also using other web tracking services in addition to Google analytics, the other being MaxCDN.
\item The website also uses an HTTP Accelerator called Varnish, which acts as a proxy server to reduce load times on the pages. 
\end{enumerate}

\section*{Wordpress Details}
\begin{enumerate}
\item The website is running wordpress version 4.6.1 which is the latest stable version.
\item They are using the wordpress theme: Bones.
\item Directory indexing is not enabled which is good for reducing the possibilities for attacks.
\item The website is running the wordpress plugin Yoast version 3.6.1 which is Yoast is an SEO plugin which major vulnerability problems \href{http://thehackernews.com/2015/03/wordpress-seo-by-yoast-plugin.html}{last year}, as well as \href{https://www.wordfence.com/blog/2016/05/yoast-seo-vulnerability/}{just a few months ago}
\item The admin login page is located \href{www.algomau.ca/wp-admin}{here}
\item Additional wordpress plugins that the site uses includes:
	\begin{enumerate}
	\item Custom Facebook Feed
	\item WC Shortcodes
	\item Malihu Custom Scrollbar
	\item Youtube Channel Gallery
	\item Magnific Popup
	\item New Royalslider
	\end{enumerate}
\item There are five authors on the WordPress website which include:
	\begin{enumerate}
	\item Nick Burnie (Author id = 0)
	\item admin\_ALGOMA (Author id = 1)
	\item Michelle Jondreau (Author id = 5)
	\item Meaghan Kent (Author id = 6)
	\item Mike Biocchi (Author id = 7)
	\end{enumerate}
\end{enumerate}


\section*{Other Information}
\begin{enumerate}
\item No malware or spam was detected, however no firewall was able to be detected either.
\item The website passes Google's safe browser check 
\end{enumerate}



  

\end{document}
